ASHA 2023 Listening Effort Data Analysis

### 2023-10-27 ASHA 2023 Analysis/data_analysis.Rmd
streamline code for data import

# Load in cleaned data

data <- rio::import("Cleaned Data/cleaned_data.csv")

intel_df <- data %>%
  dplyr::select(subject, trial, speaker, correct_words, target_number, rep_acc) %>%
  dplyr::distinct() %>%
  # removing trials with missing rep accuracy: 3 trials removed
  dplyr::mutate(rep_acc = ifelse(rep_acc == "", NA, rep_acc)) %>%
  dplyr::filter(!is.na(rep_acc))

@@

rep_acc <- intel_df %>%
  dplyr::group_by(speaker, rep_acc) %>%
  dplyr::summarize(n = n()) %>%
  tidyr::pivot_wider(names_from = rep_acc,
                     values_from = n) %>%
  dplyr::mutate(percent_accurate = accurate/(accurate + inaccurate))

@@

## Perceived Listening Effort Ratings

>>>>

# Load in cleaned data for pupil and perceived listening effort data

data <- rio::import("Cleaned Data/cleaned_data.csv") %>%
  # removing trials with missing rep accuracy: 3 trials removed
  dplyr::mutate(rep_acc = ifelse(rep_acc == "", NA, rep_acc)) %>%
  dplyr::filter(!is.na(rep_acc))

intel_df <- data %>%
  dplyr::select(subject, trial, speaker, correct_words, target_number, rep_acc) %>%
  dplyr::distinct()

@@

rep_acc <- intel_df %>%
  dplyr::group_by(speaker, rep_acc) %>%
  dplyr::summarize(n = n()) %>%
  tidyr::pivot_wider(names_from = rep_acc,
                     values_from = n) %>%
  dplyr::mutate(percent_accurate = accurate/(accurate + inaccurate)*100)

rep_acc

@@

# Perceived Listening Effort Ratings

## Descriptives

perceived_effort_df <-
